\section{Work experience}


%Experiencia 1
\parbox[t][][t]{\linewidth}{
	\parbox{\linewidth}{
		\textbf{Embedded Software Engineer}
			\hfill
			{Jan. 2022 --- \phantom{Dec. 2099}}
		}
	\smallbreak
	%\smallskip
	\parbox{\linewidth}{INVAP S.E.}
	%\smallskip
	\smallbreak
	%\bigskip
	\begin{itemize}
		\item{Argentine Primary Radar}
		\begin{itemize}
			\item{Development of reception, configuration and synchronization services in C++ of the radar backend.}
			\item{Development of real-time applications in C and FreeRTOS for R5 cores.}
			\item{I implemented the Bitbake recipes that allows the Petalinux images to be builded.}
			\item{I implemented a flavoring mechanism based on my knowledge of how Yocto works.}
			\item{I managed to create a Yocto layer system that allowed recipes to be reused within the department.}
			\item{I was able to solve the lack of a BSP for Petalinux on a board designed by a vendor, the solution mechanism I discovered is part of the company's documentation.}
			\item{Extensive use of MQTT, Protobuffer, ZMQ, keepalived, and OpenAMP.}
			\item{Development in AMD/Xilinx MPSoC.}
		\end{itemize}
		\item{SABIA-Mar satelite}
		\begin{itemize}
			\item{I designed and implemented in Python 3 the \emph{Soft-error Injection System} (SISE) tool. This system simulates the logical effects of radiation on an M4 microcontroller and allows error mitigation techniques to be evaluated.}
		\end{itemize}
	\end{itemize}
	\smallbreak
    \emph{INVAP} is the main argentine technological company (nuclear, aerospace and defense).
}

\bigskip
%Experiencia 1
\parbox[t][][t]{\linewidth}{
	\parbox{\linewidth}{
		\textbf{University Professor}
			\hfill
			{Mar. 2022 --- \phantom{Dec. 2099}}
		}
	\smallbreak
	%\smallskip
	\parbox{\linewidth}{Universidad de Morón}
	%\smallskip
	\smallbreak
	%\bigskip
	Electronics Engineering - Digital Techniques II.
	\begin{itemize}
	    \item{I modernized the program to include:}
		\begin{itemize}
			\item{Theory and practice of real-time operating systems.}
			\item{Advanced use of the C language.}
			\item{Professional workflow: git, CMake, CMocka, and Doxygen.}
		\end{itemize}
		\item{I implemented a lab from the POSIX port of FreeRTOS.}
	\end{itemize}
}

\bigskip
%Experiencia 2
\parbox[t][][t]{\linewidth}{
	\parbox{\linewidth}{
		\textbf{Embedded Software Engineer}
			\hfill
			{Feb. 2021 --- Jan. 2022}
		}
	\smallbreak
	%\smallskip
	\parbox{\linewidth}{American Traffic S.A.}
	%\smallskip
	\smallbreak
	%\bigskip
	\begin{itemize}
	    \item{Implemented a telemetry system to monitor and control all the radars of the National Highway Authority.}
	    \item{I integrated a laser profiler system for the development of the first Weigh in motion (WIM) system in Argentina.}
		\item{I implemented a program that conditions a point cloud for ingestion into the artificial intelligence that classifies vehicles.}
	\end{itemize}
	\smallbreak
    \emph{ATSA} designs and manufactures traffic technology.
}

%\bigskip
%%Experiencia 3
%\parbox[t][][t]{\linewidth}{
%	\parbox{\linewidth}{
%		\textbf{Auditor}
%			\hfill
%			{Apr. 2018 --- Dec. 2020}
%		}
%	\smallbreak
%	%\smallskip
%	\parbox{\linewidth}{Picado, Levy, De Angelis \& Asociados}
%	%\smallskip
%	\smallbreak
%	%\bigskip
%	\begin{itemize}
%	    \item{Audit and support of contractors.}
%	    \item{HFC \& GPON technologies.}
%	\end{itemize}
%	\smallbreak
%}
%
%%Experiencia 4
%\bigskip
%\parbox[t][][t]{\linewidth}{
%	{\parbox{\linewidth}{
%		\parbox{\linewidth}{
%			\textbf{Electronics Manager}
%			\hfill
%			{Apr. 2015 --- Apr. 2018}
%		}
%	}}
%	\smallbreak
%	\parbox{\linewidth}{Tecnotrans S.R.L.}
%	\smallbreak
%	\begin{itemize}
%	    \item{Production and technical service planning.}
%	    \item{Technical purchases and negotiation with suppliers (domestic and foreign).}
%	\end{itemize}
%	\smallbreak
%	\emph{Tecnotrans} designs and manufactures traffic and railway technology.
%}
%
%%Experiencia 5
%\bigskip
%\parbox[t][][t]{\linewidth}{
%	{\parbox{\linewidth}{
%		\parbox{\linewidth}{
%			\textbf{Metrology Lab Technician}
%			\hfill
%			{Aug. 2012 --- Apr. 2015}
%		}
%	}}
%	\smallbreak
%	\parbox{\linewidth}{Honeywell International, Inc.}
%	\smallbreak
%	\begin{itemize}
%	    \item{Sensor calibration.}
%	    \item{Maintenance of fire detection systems.}
%	\end{itemize}
%	\smallbreak
%    \emph{Honeywell} is an american multinational company in the Dow Jones index.
%}
%
